### 2022-07-08 src/text/2-package-subsections/analysis.tex

The gammapy.analysis sub-module provides a  high-level interface for the most
common use cases identified in gamma-ray analyses. The classes and methods
included can be used in Python scripts, notebooks or as commands within IPython
sessions. The high-level user interface can also be used to automatise
workflows driven by parameters declared in a configuration file in YAML format.
This way a full analysis can be executed via a single command line taking the
configuration file as input.

The Analysis class has the responsibility of orchestrating of the workflow
defined in the configuration (AnalysisConfig) and triggering the execution of
the AnalysisStep classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the Analysis class allows to define
custom AnalysisStep,  so ones could design and configure arbitrarily complex
wokflows.

>>>>

The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
common use cases identified in gamma-ray analyses. The classes and methods
included can be used in Python scripts, notebooks or as commands within IPython
sessions. The high-level user interface can also be used to automatise
workflows driven by parameters declared in a configuration file in YAML format.
This way a full analysis can be executed via a single command line taking the
configuration file as input.

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0...}

### 2022-07-08 src/text/2-package-subsections/astro.tex

\subsection{gammapy.astro}
\label{ssec:gammapy-astro}
\todo{Axel Donath}
Dark matter models, source population modelling

>>>>

\subsection{gammapy.astro}
\label{ssec:gammapy-astro}
\todo{Atreyee}

The \code{gammapy.astro} sub-package contains utility functions for studying physical
scenarios in high energy astrophysics. The \code{gammapy.astro.darkmatter} module
computes the so  called J-factors and the associated gamma-ray spectra expected
from annihilation of dark matter in different channels according to the recipe
described in \cite{2011JCAP...03..051C}.

In the \code{gammapy.astro.source} sub-module, dedicated classes exist for modeling
galactic \gammaray sources according to simplified physical models, eg: SNR evolution
models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the
free expansion phase \citep{2006ARA&A..44...17G} or computation
of physical parameters in a pulsar assumed to be a simple dipole.

In the \code{gammapy.astro.population} sub-module there are dedicated tools
for simulating synthetic populations based on physical models derived from
observational or theoretical considerations for different classes of Galactic
VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C},
pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y}
and gamma-ray binaries.

While the present list of use cases is rather preliminary, this can be enriched
with time with by users and/or developers according to future needs.

### 2022-07-08 src/text/2-package-subsections/catalog.tex

Comprehensive source catalogs are increasingly being provided by many high
energy astrophysics experiments. gammapy.catalog provides a convenient access
to some common gamma-ray catalogs. A global catalog table is provided, along
with source models flux points and light curves (if available) for individual
objects, which are internally created from the supplied FITS tables. This
module works independently from the rest of the package, and the required
catalogs are supplied in GAMMAPY\_DATA. Presently, catalogs from Fermi-LAT
(standard~\citep{3FGL, 4FGL} and high energy~\citep{2FHL, 3FHL}), H.E.S.S.
galactic plane survey~\citep{HGPS}, HAWC~\citep{2HWC, 3HWC} and gamma-cat
~\citep{gamma-cat}; an open source gamma ray catalog combining information from
multiple catalogs) are supported.

>>>>

Comprehensive source catalogs are increasingly being provided by many high
energy astrophysics experiments. gammapy.catalog provides a convenient access
to some common gamma-ray catalogs. A global catalog table is provided, along
with source models flux points and light curves (if available) for individual
objects, which are internally created from the supplied FITS tables. This
module works independently from the rest of the package, and the required
catalogs are supplied in GAMMAPY\_DATA. The overview of currenly supported
catalogs and the correponding \gammapy classes is shown in Table~\ref{tab:catalogs}.
Newly released relevant catalogs will be added in future.

\begin{table*}
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & Third catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & Fourth catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & Second catalog high energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & Third catalog high energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & Second catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & Third catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Built-in catalogs.}
\end{table*}

### 2022-07-08 src/text/2-package-subsections/data.tex

\subsection{gammapy.data}
\label{ssec:gammapy-data}
\todo{Cosimo Nigro}
The \verb|gammapy.data| sub-package provides access to DL3 level data and
observation handling.

@@

	\caption{Using gammapy.data to access DL3 level data with a DataStore}
	\label{fig*:minted:gp_data}
\end{figure}

>>>>

\subsection{gammapy.data}
\label{ssec:gammapy-data}
\todo{Cosimo Nigro}

@@

	\caption{Using \code{gammapy.data} to access DL3 level data with a \code{DataStore} object.
    Individual observations can be accessed by their unique integer observation id number.
    The actual events and instrument response functions can be accessed
    as attributes on the \code{Observation} object, such as \code{.events}
    or \code{.aeff} for the effective area information.
    }
	\label{fig*:minted:gp_data}
\end{figure}

As illustrated in Fig.~\ref{fig:data_flow}, the \code{gammapy.data} sub-package
implements the interface to the lowest data level, providing the input interface to gamma-ray
data. The \gammapy data model follows the \gadf specifications
(Sec.~\ref{sec:introduction}), therefore gamma-ray data compliant with those
can be directly read with the package. Version X.X of the \gadf specification
is supported in this release version. As both the \gadf data model and \gammapy
were initially conceived for \iact data analysis, input data are typically
grouped in \code{Observations}, corresponding to stable periods of data
aquisitions (typically $20 - 30\,{\rm min}$). A \code{DataStore} object,
gathering a collection of observations, can be created providing ancillary
files containing information about the telescope observation mode and the
content of the data unit of each file. The \code{DataStore} allows for
selecting a list of observations based on specific filters. As an illustrative
example, Fig.~\ref{fig*:minted:gp_data} shows how to create a
\code{DataStore} and how to obtain the observations corresponding to given
identification numbers (IDs).

The so-called DL3 files represented by the \code{Observation} class consist
of two types of elements: a list of gamma-ray events with relevant physical
quantities for the successive analysis (estimated energy, direction and arrival
times) that is handled by the \code{EventList} class and an instrument
response function (IRF), providing the response of the system, typically
factorised in independent components (see the description in
Sec.~\ref{ssec:gammapy-irf}). The separate handling of event lists and IRFs
additionally allows for data from other gamma-ray instruments to be read. For
example, to read \fermi data, the user can read separately their event list
(already compliant with the \gadf specifications) and then find the appropriate
IRF class representing the response functions provided by \fermi, see
Sec.~\ref{ssec:fermi}.

### 2022-07-08 src/text/2-package-subsections/estimators.tex

The \verb|gammapy.estimators| sub-module features methods to compute flux
points, light curves, flux maps, flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \verb|MapDataset| are grouped into
larger bins. The norm of the best fit "reference" spectral
model is fitted ("scaled") in the  restricted data range only.

The base class of all algorithms is the `Estimator`  class.

Signifiance is estimated based on hypothesis \
testing against the background only model. This allows
to assign a significance to the given flux bin.
In addition to the best fit flux norm all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both,
the so-called TS value.
From the TS value the significance of the
significance of the measured signal and associated flux
can be derived.

@@

The result of the flux point estimation are either stored in a
\verb|FluxMaps| or \verb|FluxPoints| object. Both objects
are based on an internal representation of the flux which is
independent of the SED type. The flux is represented by a
the reference spectral model and an array of
normalisation values given in energy, time and spatial bins,
which factorise the deviation of the flux in the given
bin form the reference spectral model. This allows
user to conveniently transform between different
SED types. See Table \ref{tab:sed_types}.
The actual flux values are obtained by mutiplication of the norm with the
reference flux.

@@

Both result objects support the possibility to serialise
the data into multiple formats. This includes the
GADF SED (reference?) format, FITS based ND sky-maps
and formats compatible with Astropy's \verb|Table| and
\verb|BinnedTimeSeries| data structures. This allows
users to directly further analyse the results, e.g.
standard algorithms for time analysis such as
computing Lomb-Scargle periodograms or Bayesian
blocks for time series.

So far \gammapy does not support "unfolding" of \gammaray spectra.
Methods for this will be implemented in future version of \gammapy.

\begin{itemize}
	\item Regrouping of dataset bins in time, energy etc.
	\item "Forward folding" / "Backward folding": but there is no
	      difference between the two, backwards folding is forward folding with one bin
	\item Likelihood profiles \item Uniform N-dimensional data structure \item
	      Uniform API for plotting etc. \item \verb|FluxMaps| and \verb|FluxPoints| \item
	      Serialisation to multiple formats, Astropy's \verb|Table| and
	      \verb|BinnedTimeSeries|
	\item Additional quantities for debugging, such as predicted counts, fit convergence,
	      sum of fit statistics \item \end{itemize}

Code example ~\ref{fig*:minted:gp_estimators} shows how to use
the \verb|TSMapEstimator| with a given input `MapDataset`.
In addition to the model it allows to specify the energy
bisn of the resulting flux and TS maps.

\begin{figure}
	\import{code-examples/generated/}{gp_estimators}
	\caption{Using the TSMapEstimator from gammapy.estimators to compute a
		sqrt(TS) map.} \label{fig*:minted:gp_estimators} \end{figure}

>>>>

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps, flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. The norm of the best fit "reference" spectral
model is fitted ("scaled") in the  restricted data range only.

The base class of all algorithms is the \code{Estimator}  class.

Signifiance is estimated based on hypothesis
testing against the background only model. This allows
to assign a significance to the given flux bin.
In addition to the best fit flux norm all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both,
the so-called TS value.
From the TS value the significance of the
significance of the measured signal and associated flux
can be derived.

@@

The result of the flux point estimation are either stored in a
\code{FluxMaps} or \code{FluxPoints} object. Both objects
are based on an internal representation of the flux which is
independent of the SED type. The flux is represented by a
the reference spectral model and an array of
normalisation values given in energy, time and spatial bins,
which factorise the deviation of the flux in the given
bin form the reference spectral model. This allows
user to conveniently transform between different
SED types. See Table \ref{tab:sed_types}.
The actual flux values are obtained by mutiplication of the norm with the
reference flux.

@@

Both result objects support the possibility to serialise
the data into multiple formats. This includes the
GADF SED (reference?) format, FITS based ND sky-maps
and formats compatible with Astropy's \code{Table} and
\code{BinnedTimeSeries} data structures. This allows
users to directly further analyse the results, e.g.
standard algorithms for time analysis such as
computing Lomb-Scargle periodograms or Bayesian
blocks for time series. So far \gammapy does not
support "unfolding" of \gammaray spectra.
Methods for this will be implemented in future version of \gammapy.

Code example ~\ref{fig*:minted:gp_estimators} shows how to use
the \code{TSMapEstimator} objects with a given input \code{MapDataset}.
In addition to the model it allows to specify the energy
bins of the resulting flux and TS maps.

\begin{figure}
	\import{code-examples/generated/}{gp_estimators}
	\caption{Using the \code{TSMapEstimator} object from \code{gammapy.estimators} to compute a
        a flux, flux upper limits and TS map. The additional parameters \code{n\_sigma}
        and \code{n\_sigma\_ul} define the confidence levels (in multiples of the normal distribution width)
        of the flux error and and flux upper limit maps respectively.
    }
    \label{fig*:minted:gp_estimators}
\end{figure}

### 2022-07-08 src/text/2-package-subsections/maps.tex

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes that represent data
structures associated with a set of coordinates or a region on a sphere. In
addition it allows to handle an arbitrary number of non-spatial data
dimensions, such as time or energy. It is organized around three types of
structures: geometries, sky-maps and map axes, which inherit from the base
classes Geom, Map and MapAxis respectively.

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as non-linear step sizes.

@@

% itemize because it helps me write, could also just be paragraphs...
\begin{itemize}
	\item \textbf{WCS: } The FITS WCS pixelization supports a different
	      number of projections to represent celestial spherical coordinates in a regular
	      rectangular grid. Gammapy provides full support to data structures using this
	      pixelization scheme.
	 \item \textbf{HEALPix: } This pixelization provides a
	      subdivision of a sphere in which each pixel covers the same surface area as
	      every other pixel. As a consequence, however, pixel shapes are no longer
	      rectangular, or regular. \gammapy provides limited support to HEALPix-based
	      maps, relying in some cases on projections to a local WCS grid. 
   \item \textbf{Region geometries: } In this case, instead of a fine spatial grid
	      dividing a rectangular sky region, the spatial dimension is reduced to a single
	      bin with an arbitrary shape, describing a region in the sky with that same
	      shape. Typically they are is used together with a non-spatial dimension, for
	      example an energy axis, to represent how a quantity varies in that dimension
	      inside the corresponding region. \end{itemize}

Additionally, the MapAxis class provides a uniform API for axes representing
bins on any physical quantity, such as energy or angular offset. The special
case of time is covered by the dedicated TimeMapAxis, which allows time bins to
be non-contiguous, as it is often the case with observation time-stamps. The
generic class LabelMapAxis allows the creation of axes for non-numeric entries.

	\caption{Using gammapy.maps to create a WCS, a HEALPix and a region
		map. Note the uniform API for map creation.} \label{ig*:minted:gp_maps}
\end{figure}

>>>>

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
\todo{Laura Olivera-Nieto}

	\caption{Using \code{gammapy.maps} to create a WCS, a HEALPix and a region
		based data structures. The initialisation parameters include
        consistently the positions of the center of the map, the pixel
        size, the extend of the map as well as the energy axis definition.
        } \label{ig*:minted:gp_maps}
\end{figure}

The \code{gammapy.maps} sub-package provides classes that represent data
structures associated with a set of coordinates or a region on a sphere. In
addition it allows to handle an arbitrary number of non-spatial data
dimensions, such as time or energy. It is organized around three types of
structures: geometries, sky-maps and map axes, which inherit from the base
classes \code{Geom}, \code{Map} and \code{MapAxis} respectively.

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a Numpy data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as define non-linear spaced bins.

@@

% itemize because it helps me write, could also just be paragraphs...
\paragraph{WCS:}
The FITS WCS pixelization supports a different
number of projections to represent celestial spherical coordinates in a regular
rectangular grid. Gammapy provides full support to data structures using this
pixelization scheme.

\paragraph{HEALPix:}
This pixelization provides a
subdivision of a sphere in which each pixel covers the same surface area as
every other pixel. As a consequence, however, pixel shapes are no longer
rectangular, or regular. \gammapy provides limited support to HEALPix-based
maps, relying in some cases on projections to a local WCS grid.

\paragraph{Region:} In this case, instead of a fine spatial grid
dividing a rectangular sky region, the spatial dimension is reduced to a single
bin with an arbitrary shape, describing a region in the sky with that same
shape. Typically they are is used together with a non-spatial dimension, for
example an energy axis, to represent how a quantity varies in that dimension
inside the corresponding region.

Additionally, the \code{MapAxis} class provides a uniform API for axes representing
bins on any physical quantity, such as energy or angular offset. The special
case of time is covered by the dedicated \code{TimeMapAxis}, which allows time bins to
be non-contiguous, as it is often the case with observation time-stamps. The
generic class \code{LabelMapAxis} allows the creation of axes for non-numeric
entries.

### 2022-07-08 src/text/2-package-subsections/modeling.tex
Fix section level for modeling section
Fix pre-commit hooks

gammapy.modeling contains all the functionality related to modeling and fitting
data. This includes spectral, spatial and temporal model classes, as well as
the fit and parameter API.

\subsection{Models}
\label{ssec:models}

@@

\begin{itemize}
	\item SpectralModel: models to describe spectral shapes of sources
	\item SpatialModel: models to describe spatial shapes (morphologies) of sources
	\item TemporalModel: models to describe temporal flux evolution of sources, such as
	      light and phase curves

@@

The  Spectral Models include a special class of Normed models, which have a
dimension-less normalisation. These spectral models feature a norm parameter
instead of amplitude and are named using the NormSpectralModel suffix. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding a EBL correction to some analytic
model. The analytic Spatial models are all normalized such as they integrate to
unity over the sky but the template Spatial models may not, so in that special
case they have to be combined with a NormSpectralModel.

The SkyModel is a factorised model that combine the spectral, spatial and
temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple SkyModel components, Gammapy
has a Models class.

The model gallery provides a visual overview of the available models in
Gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\cite{naima}. The modeling framework can be easily extended with
user-defined models. For example agnpy models that describe leptonic radiative
processes in jetted Active Galactic Nuclei (AGN) can wrapped into
gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .

\begin{figure}
	\import{code-examples/generated/}{gp_models}
	\caption{Using gammapy.modeling.models}
	\label{fig*:minted:gp_models}
\end{figure}

\subsection{Fit}
\label{ssec:fit}

The Fit class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a Datasets object, which
in turn is connected to a Models object containing the model parameters in its
Parameters object.  Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
examples are given in the tutorials.

>>>>

\code{gammapy.modeling} contains all the functionality related to modeling and fitting
data. This includes spectral, spatial and temporal model classes, as well as
the fit and parameter API.

\subsubsection{Models}
\label{sssec:models}

@@

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves

@@

The spectral models include a special class of normed models, which have a
dimension-less normalisation. These spectral models feature a norm parameter
instead of amplitude and are named using the NormSpectralModel suffix. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding a EBL correction to some analytic
model. The analytic spatial models are all normalized such as they integrate to
unity over the sky but the template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

The \code{SkyModel} object represents factorised model that combine the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models  commonly used in gamma-ray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\cite{naima}. The modeling framework can be easily extended with
user-defined models. For example agnpy models that describe leptonic radiative
processes in jetted Active Galactic Nuclei (AGN) can wrapped into
\gammapy~\citep[see section3.5 of ][]{2021arXiv211214573N} .

\begin{figure}
	\import{code-examples/generated/}{gp_models}
	\caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an addtional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model.
    }
	\label{fig*:minted:gp_models}
\end{figure}

\subsubsection{Fit}
\label{sssec:fit}

The \code{Fit} class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a Datasets object, which
in turn is connected to a Models object containing the model parameters in its
Parameters object. Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
examples are given in the tutorials.

\todo{Add fit code example...}

### 2022-07-08 src/text/3-applications-subsections/1D-analysis.tex
Reformat text files

\subsection{1D Analysis}
\label{ssec:1d-analysis}
\todo{Axel}
One of the most common analysis cases in gamma-ray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called aperture photometry.
The spectrum is typically measured in two steps: first a parametric
spectral model is fitted to the data and secondly flux points are computed
in a pre-defined set of energy bins.
The result of such an analysis performed on three simulated CTA observations
is shown in Fig.~\ref{fig:cta_galactic_center}.
In this case the spectrum was measured in a circular aperture centered
on the Galactic Center, in \gammaray~astronomy often called "on region".
For such analysis the users first chooses a region of interest
and energy binning, both defined by a `RegionGeom`.
In a second step the events and instrument response are binned into
maps of this geometry, by the `SpectrumDatasetMaker`.
All the data and reduced instrument response are bundled into a
`SpectrumDataset`.
To estimate the expected background in the on region a "reflected regions"
background method was used~\cite{Berge07}, represented in \gammapy
by the `ReflectedRegionsBackgroundMaker` class.
The resulting reflected regions are illustrated for all three observations
on top of the map of counts.
After reduction of the data it was modelled using a forward-folding
method and a power-law spectral shape, using the `PowerLawSpectralModel`
and `Fit` class.
Based on this best fit model the final flux points and
corresponding log-likleihood profiles are computed using
the `FluxPointsEstimator`.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
        Example spectral analysis of the Galactic Center for three simulated CTA observations.
        The left image shows the maps of counts with the measurement region and background
        regions overlaid in different colors. The right image shows the resulting spectral
        points and their corresponding log-likelihood profiles.
    }
	\label{fig:cta_galactic_center}
\end{figure*}

>>>>

\subsection{1D Analysis}
\label{ssec:1d-analysis}
\todo{Axel}
One of the most common analysis cases in gamma-ray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called aperture photometry. The spectrum is typically measured
in two steps: first a parametric spectral model is fitted to the data and
secondly flux points are computed in a pre-defined set of energy bins. The
result of such an analysis performed on three simulated CTA observations is
shown in Fig.~\ref{fig:cta_galactic_center}. In this case the spectrum was
measured in a circular aperture centered on the Galactic Center, in
\gammaray~astronomy often called "on region". For such analysis the users first
chooses a region of interest and energy binning, both defined by a
\code{RegionGeom}. In a second step the events and instrument response are binned
into maps of this geometry, by the \code{SpectrumDatasetMaker}. All the data and
reduced instrument response are bundled into a \code{SpectrumDataset}. To estimate
the expected background in the on region a "reflected regions" background
method was used~\cite{Berge07}, represented in \gammapy by the
\code{ReflectedRegionsBackgroundMaker} class. The resulting reflected regions are
illustrated for all three observations on top of the map of counts. After
reduction of the data it was modelled using a forward-folding method and a
power-law spectral shape, using the \code{PowerLawSpectralModel} and \code{Fit} class.
Based on this best fit model the final flux points and corresponding
log-likelihood profiles are computed using the \code{FluxPointsEstimator}.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
		Example spectral analysis of the Galactic Center for three simulated CTA
		observations. The left image shows the maps of counts with the measurement
		region and background regions overlaid in different colors. The right image
		shows the resulting spectral points and their corresponding log-likelihood
		profiles.} \label{fig:cta_galactic_center} \end{figure*}
